Effective multi-body SU($N$)-symmetric interactions of ultracold fermionic atoms on a 3-D lattice

### 2019-02-14 multi_body_interactions/papers/theory/reviews_NJP/referee_response_1.tex

% general physics / math packages and commands
\usepackage{physics,amsmath,amssymb,braket,dsfont}
\renewcommand{\t}{\text} % text in math mode
\newcommand{\f}{\dfrac} % shorthand for fractions
\newcommand{\p}[1]{\left(#1\right)} % parenthesis
\renewcommand{\sp}[1]{\left[#1\right]} % square parenthesis
\renewcommand{\set}[1]{\left\{#1\right\}} % curly parenthesis
\newcommand{\bk}{\braket} % shorthand for braket

\renewcommand{\d}{\text{d}}
\newcommand{\g}{\text{g}}
\newcommand{\e}{\text{e}}
\newcommand{\x}{\text{x}}
\newcommand{\y}{\text{y}}
\newcommand{\z}{\text{z}}

\renewcommand{\c}{\hat{c}}
\newcommand{\n}{\hat{n}}

\newcommand{\A}{\mathcal{A}}
\newcommand{\B}{\mathcal{B}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\E}{\mathcal{E}}
\newcommand{\G}{\mathcal{G}}
\renewcommand{\H}{\mathcal{H}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\K}{\mathcal{K}}
\renewcommand{\L}{\mathcal{L}}
\newcommand{\M}{\mathcal{M}}
\newcommand{\N}{\mathcal{N}}
\renewcommand{\O}{\mathcal{O}}
\renewcommand{\P}{\mathcal{P}}
\newcommand{\Q}{\mathcal{Q}}
\renewcommand{\S}{\mathcal{S}}
\newcommand{\U}{\mathcal{U}}

\newcommand{\1}{\mathds{1}}

\newcommand{\mA}{m_{\text{A}}} % symbol for the mass of an atom

% "left vector" arrow; requires tikz package
\newcommand{\lvec}[1]
{\reflectbox{\ensuremath{\vec{\reflectbox{\ensuremath{#1}}}}}}

% figures
\usepackage{graphicx} % for figures
\usepackage{grffile} % help latex properly identify figure extensions
\graphicspath{{./figures/}} % set path for all figures
\usepackage[caption=false]{subfig} % subfigures (via \subfloat[]{})

% inline lists
\usepackage[inline]{enumitem}

@@

% for feynman diagrams
\usepackage{tikz,tikz-feynman}
\tikzset{
  baseline = (current bounding box.center)
}
\tikzfeynmanset{
  compat = 1.1.0,
  every feynman = {/tikzfeynman/small}
}
\newcommand{\shrink}[1]{\scalebox{0.8}{#1}} % for smaller diagrams

% color definitions (used in a figure)
\usepackage{xcolor}
\definecolor{lightblue}{RGB}{31,119,180}
\definecolor{orange}{RGB}{255,127,14}
\definecolor{green}{RGB}{44,160,44}
\definecolor{lightred}{RGB}{214,39,40}

% proper coloring inside math environment
\makeatletter
\def\mathcolor#1#{\@mathcolor{#1}}
\def\@mathcolor#1#2#3{
  \protect\leavevmode
  \begingroup
    \color#1{#2}#3
  \endgroup
}
\makeatother
\newcommand{\bmu}{\mathcolor{lightblue}{\mu}}
\newcommand{\onu}{\mathcolor{orange}{\nu}}
\newcommand{\grho}{\mathcolor{green}{\rho}}
\newcommand{\re}{\mathcolor{lightred}{\text{e}}}

% leave a note in the text, visible in the compiled document
\newcommand{\note}[1]{\textcolor{red}{#1}}

@@

  \red{\begin{align*}
      H_M = \sum_{\abs{\set{\mu_j}}=M}
      \p{U_{M,\g} \prod_{\alpha=1}^M \n_{\mu_\alpha,\g}
        + U_{M,+} \n_{\mu_1,\e} \prod_{\alpha=2}^M \n_{\mu_\alpha,\g}
        + U_{M,-} \c_{\mu_1,\g}^\dag \c_{\mu_2,\e}^\dag
        \c_{\mu_2,\g} \c_{\mu_1,\e} \prod_{\alpha=3}^M \n_{\mu_\alpha,\g}},
      \tag{42}
    \end{align*}}

  to:

  \green{\begin{align*}
      H_M = \sum_{\abs{\set{\mu_j}}=M}
      \p{U_{M,\g} \n_{\mu_1,\g} \n_{\mu_2,\g}
        + U_{M,+} \n_{\mu_1,\e} \n_{\mu_2,\g}
        + U_{M,-} \c_{\mu_1,\g}^\dag \c_{\mu_2,\e}^\dag
        \c_{\mu_2,\g} \c_{\mu_1,\e}}
      \prod_{\alpha=3}^M \n_{\mu_\alpha,\g},
      \tag{44}
    \end{align*}}

  Note that the new equation number is 44 due to the addition of two
  new equations in response to point \ref{pt:divergence} below.  We
  have made the same change to Eq.~(F1), which is included in Appendix
  F for quick reference.  Appendix F and Eq.~(F1) are respectively
  Appendix G and Eq.~(G1) in the revised version of our manuscript, as
  we have added a new appendix in one of our responses to referee 2.

@@

  by:

  \green{The renormalization condition in (16) explicitly fixes $G_X$
    to the net effective coupling constants in any given setting.
    Instead of using free-space coupling constants to compute
    interaction energies in a lattice, we must therefore first compute
    the effective coupling constants $G_X^{\t{lattice}}\p{\U}$, which
    now depend on the lattice depth $\U$, and in turn use these
    effective coupling constants to compute interaction energies.}

  We have also added a paragraph explaining where and why counter-term
  diagrams should appear in our effective theory, in particular
  explaining why counter-terms do not appear at leading order for
  effective $M$-body interactions.  This new paragraph is inserted
  between lines 23 and 24 on page 13:

  \green{Second, the renormalization condition in (16) implies that
    the counter terms $\tilde G_X$ are second order in the coupling
    constants $G_X$, i.e.~$\tilde G_X\sim G_X^2$.  Although the
    effective Hamiltonian expansions in (13) and (14) are organized in
    powers of the interaction Hamiltonian $H_{\t{int}}$, the couplings
    $G_X$ are the ``small'' parameters in which we can formally
    organize a perturbation theory; more specifically, the formally
    small quantities organizing our perturbation theory are two-body
    ground-state interaction energies (proportional to the couplings
    $G_X$) divided by the spectral gap of the single-atom Hamiltonian
    $H_0$ (see Appendix F).  If $M$ atoms can only couple through
    terms represented by a $p$-vertex diagrams for
    $p\ge p_M^{\t{min}}$, then the leading order contribution to
    $M$-body interactions is order $p_M^{\t{min}}$ in the couplings
    $G_X$.  If the same $p_M^{\t{min}}$-vertex diagrams involve any
    counter-terms, however, then these diagrams are at least order
    $p_M^{\t{min}}+1$ in the couplings $G_X$.  Counter-terms therefore
    only appear at next-to-leading order (NLO) in the calculation of
    effective $M$-body interactions.}

  Note that Appendix F referenced above is a new appendix we have
  added in our response to referee 2.  To reflect the addition of the
  above paragraph, we have modified the text on page 13, line 7:

### 2019-02-14 multi_body_interactions/papers/theory/paper.tex
added last of the revisions to the paper (pre-markup by AMR)

Second, the renormalization condition in \eqref{eq:counter_term}
implies that the counter terms $\tilde G_X$ are second order in the
coupling constants $G_X$, i.e.~$\tilde G_X\sim G_X^2$.  Although the
effective Hamiltonian expansions in \eqref{eq:H_int_1_2} and
\eqref{eq:H_int_3} are organized in powers of the interaction
Hamiltonian $H_{\t{int}}$, the couplings $G_X$ are the ``small''
parameters in which we can formally organize a perturbation theory;
more specifically, the formally small quantities organizing our
perturbation theory are two-body ground-state interaction energies
(proportional to the couplings $G_X$) divided by the spectral gap of
the single-atom Hamiltonian $H_0$.  If $M$ atoms can only couple
through terms represented by a $p$-vertex diagrams for
$p\ge p_M^{\t{min}}$, then the leading order contribution to $M$-body
interactions is order $p_M^{\t{min}}$ in the couplings $G_X$.  If the
same $p_M^{\t{min}}$-vertex diagrams involve any counter-terms,
however, then these diagrams are at least order $p_M^{\t{min}}+1$ in
the couplings $G_X$.  Counter-terms therefore only appear at
next-to-leading order (NLO) in the calculation of effective $M$-body
interactions.

@@

Identifying peaks in excitation spectra such as in figure
\ref{fig:sweep} constitutes a measurement of many-body excitation
energies, which was performed in ref.~\cite{goban2018emergence} to
detect signatures of effective multi-body interactions.  Figure
\ref{fig:shifts} shows a comparison between
\begin{enumerate*}
\item experimental measurements of the many-body excitation energies
  $\Delta_{NX}$ for all $\p{N,X}\in\set{3,4,5}\times\set{+,-}$ at
  various lattice depths $\U$, and
\item the corresponding values of $\Delta_{NX}$ predicted by the
  low-energy effective theory at different orders in the coupling
  constants.
\end{enumerate*}
A known source of error in our effective theory comes from neglecting
the inter-site matrix elements of all Hamiltonians.  This error is
discussed in Appendix \ref{sec:error}, and leads to theoretical
uncertainties represented by error bars on the $\O\p{G^3}$ theory in
figure \ref{fig:shifts}.  A summary of figure \ref{fig:shifts} is
provided in figure \ref{fig:shifts_summary}.  We note that many-body
interaction energy shifts are smaller for asymmetric ($-$) states than
symmetric ($+$) ones due to the competition between contributions of
opposite sign in the asymmetric case (see rows 2 and 3 of table
\ref{tab:eigen}).

The results in figures \ref{fig:shifts} and \ref{fig:shifts_summary}
highlight a few important points about ultracold, high-density
${}^{87}$Sr experiments and our low-energy effective theory.  First,
these experiments exhibit clear signatures of multi-body interactions,
as evidenced by a stark disagreement between the observed many-body
excitation energies $\Delta_{NX}$ and those that are predicted by the
two-body $\O\p{G}$ theory.  Multi-body interactions are thus crucial
for understanding these high-density experiments in the context of a
single-band Hubbard model, which naturally arises in the
zero-temperature limit when all atoms occupy their motional ground
state.  Second, the inter-atomic interactions in these experiments are
strong enough to require going beyond leading order for the
description of multi-body interactions in the low-energy effective
theory.  As experiments begin to work with more atoms and shallower
lattices, therefore, reliably predicting interaction energies may
require going to yet higher orders in perturbation theory.  Due to a
combinatorial explosion of the number of diagrams which appear at
increasing orders in the effective theory, however, we need more
systematic methods to compute effective multi-body Hamiltonians at
fourth order.  In any case, we are agnostic as to whether such a
calculation would provide better agreement between experiment and
theory without first performing a detailed analysis of systematic
errors.

@@

\section*{Appendices}
\appendix

@@

@@

The $M$-body Hamiltonians addressing low-lying orbital state
excitations can be written in the form
\begin{align}
  H_M = \sum_{\abs{\set{\mu_j}}=M}
  \p{U_{M,\g} \n_{\mu_1,\g} \n_{\mu_2,\g}
    + U_{M,+} \n_{\mu_1,\e} \n_{\mu_2,\g}
    + U_{M,-} \c_{\mu_1,\g}^\dag \c_{\mu_2,\e}^\dag
    \c_{\mu_2,\g} \c_{\mu_1,\e}}
  \prod_{\alpha=3}^M \n_{\mu_\alpha,\g},
\end{align}
where the coefficients can be expanded as
$U_{MX} = \sum_p U_{MX}^{(p)}$ with terms $U_{MX}^{(p)}$ at order $p$
in the coupling constants $G_Y$.  The terms $U_{MX}^{(p)}$ can be
determined from the $M$-body $p$-order Hamiltonians $H_M^{(p)}$
derived in section \ref{sec:low_energy}, i.e.~in \eqref{eq:H_2},
\eqref{eq:H_3_2}, \eqref{eq:H_3_3}, and \eqref{eq:H_4_3}.  For the
effective 2-, 3-, and 4-body Hamiltonians through third order in the
coupling constants, the coefficients are
\begin{align}
  U_{2,\g} = \f12 \alpha_2^{(1)} G_\g,
  &&
  U_{2,+} = \alpha_2^{(1)} G_+,
  &&
  U_{2,-} = \alpha_2^{(1)} G_-,
\end{align}
\begin{align}
  U_{3,\g}^{(2)} = - \alpha_3^{(2)} G_\g^2,
  &&
  U_{3,+}^{(2)} = - \alpha_3^{(2)} G_+ \p{G_+ + 2 G_\g},
\end{align}
\begin{align}
  U_{3,-}^{(2)} = - \alpha_3^{(2)} G_- \p{2 G_+ + G_- + 2 G_\g},
\end{align}
\begin{align}
  U_{3,\g}^{(3)}
  = \p{\alpha_3^{(3)} - \alpha_5^{(3)}} 2 G_\g^3
  - \p{\alpha_{4,3}^{(3)} + \alpha_5^{(3)}} G_\g^3,
\end{align}
\begin{align}
  U_{3,+}^{(3)}
  &= \p{\alpha_3^{(3)} - \alpha_5^{(3)}} \p{G_+^3 + 4 G_+^2 G_\g
    + G_+ G_-^2 + G_+ G_\g^2 + G_-^3 + G_-^2 G_\g} \nonumber \\
  &\quad - \p{\alpha_{4,3}^{(3)} + \alpha_5^{(3)}}
  \p{G_+^3 + G_+^2 G_\g + G_+ G_-^2 + G_+ G_\g^2 + G_-^2 G_\g},
\end{align}
\begin{align}
  U_{3,-}^{(3)}
  &= \p{\alpha_3^{(3)} - \alpha_5^{(3)}} G_- \p{3 G_+^2
    + 2 G_+ G_- + 8 G_+ G_\g + 3 G_- G_\g + G_\g^2} \nonumber \\
  &\quad - \p{\alpha_{4,3}^{(3)} + \alpha_5^{(3)}}
  G_- \p{3 G_+^2 + 2 G_+ G_- + 2 G_+ G_\g + G_-^2 + G_\g^2},
\end{align}
\begin{align}
  U_{4,\g}^{(3)}
  = \p{\alpha_{4,1}^{(3)} - \alpha_5^{(3)}} G_\g^3
  + \p{\alpha_{4,2}^{(3)} - \alpha_5^{(3)}} 2 G_\g^3,
\end{align}
\begin{align}
  U_{4,+}^{(3)}
  &= \p{\alpha_{4,1}^{(3)} - \alpha_5^{(3)}}
  2 G_+ G_\g \p{G_+ + G_\g} \nonumber \\
  &\quad + \p{\alpha_{4,2}^{(3)} - \alpha_5^{(3)}}
  G_+ \p{G_+^2 + 2 G_+ G_\g + 5 G_\g^2},
\end{align}
\begin{align}
  U_{4,-}^{(3)}
  &= \p{\alpha_{4,1}^{(3)} - \alpha_5^{(3)}}
  2 G_- G_\g \p{2 G_+ + G_- + G_\g} \nonumber \\
  &\quad + \p{\alpha_{4,2}^{(3)} - \alpha_5^{(3)}}
  G_- \p{3 G_+^2 + 3 G_+ G_- + 4 G_+ G_\g + G_-^2
    + 2 G_- G_\g + 5 G_\g^2},
\end{align}
In terms of the spatial overlap integrals defined in \eqref{eq:K_klmn}
and \eqref{eq:K}, the prefactors $\alpha_X^{(p)}$ on the coefficients
$U_X^{(p)}$ are
\begin{align}
  \alpha_2^{(1)} \equiv K,
  &&
  \alpha_3^{(2)} \equiv \sum_{n>0} \f{K_n^2}{E_n},
  &&
  \alpha_3^{(3)} \equiv \sum_{\substack{\ell+m>0\\\ell+n>0}}
  \f{K_{\ell m} K^m_n K_{\ell n}}{E_{\ell m} E_{\ell n}},
\end{align}
\begin{align}
  \alpha_{4,1}^{(3)}
  \equiv \sum_{\substack{m\ge0\\n>0}} \f{K_{mn} K_m K_n}{E_{mn} E_n},
  &&
  \alpha_{4,2}^{(3)}
  \equiv \sum_{m,n>0} \f{K_m K^m_n K_n}{E_m E_n},
  &&
  \alpha_{4,3}^{(3)}
  \equiv K \sum_{m+n>0} \f{K_{mn}^2}{E_{mn}^2},
\end{align}
\begin{align}
  \alpha_5^{(3)}
  \equiv  K \sum_{n>0} \f{K_n^2}{E_n^2}.
\end{align}

>>>>

Second, the renormalization condition in \eqref{eq:counter_term}
implies that the counter terms $\tilde G_X$ are second order in the
coupling constants $G_X$, i.e.~$\tilde G_X\sim G_X^2$.  Although the
effective Hamiltonian expansions in \eqref{eq:H_int_1_2} and
\eqref{eq:H_int_3} are organized in powers of the interaction
Hamiltonian $H_{\t{int}}$, the couplings $G_X$ are the ``small''
parameters in which we can formally organize a perturbation theory;
more specifically, the formally small quantities organizing our
perturbation theory are two-body ground-state interaction energies
(proportional to the couplings $G_X$) divided by the spectral gap of
the single-atom Hamiltonian $H_0$ (see Appendix
\ref{sec:pert_params}).  If $M$ atoms can only couple through terms
represented by a $p$-vertex diagrams for $p\ge p_M^{\t{min}}$, then
the leading order contribution to $M$-body interactions is order
$p_M^{\t{min}}$ in the couplings $G_X$.  If the same
$p_M^{\t{min}}$-vertex diagrams involve any counter-terms, however,
then these diagrams are at least order $p_M^{\t{min}}+1$ in the
couplings $G_X$.  Counter-terms therefore only appear at
next-to-leading order (NLO) in the calculation of effective $M$-body
interactions.

@@

Identifying peaks in excitation spectra such as in figure
\ref{fig:sweep} constitutes a measurement of many-body excitation
energies, which was performed in ref.~\cite{goban2018emergence} to
detect signatures of effective multi-body interactions.  Figure
\ref{fig:shifts} shows a comparison between
\begin{enumerate*}
\item experimental measurements of the many-body excitation energies
  $\Delta_{NX}$ for all $\p{N,X}\in\set{3,4,5}\times\set{+,-}$ at
  various mean lattice depths $\U$, and
\item the corresponding values of $\Delta_{NX}$ predicted by the
  low-energy effective theory at different orders in the coupling
  constants.
\end{enumerate*}
A known source of error in our effective theory comes from neglecting
the inter-site matrix elements of all Hamiltonians.  This error is
discussed in Appendix \ref{sec:error}, and leads to theoretical
uncertainties represented by error bars on the $\O\p{G^3}$ theory in
figure \ref{fig:shifts}.  A summary of figure \ref{fig:shifts} is
provided in figure \ref{fig:shifts_summary}.  We note that many-body
interaction energy shifts are smaller for asymmetric ($-$) states than
symmetric ($+$) ones due to the competition between contributions of
opposite sign in the asymmetric case (see rows 2 and 3 of table
\ref{tab:eigen}).

The results in figures \ref{fig:shifts} and \ref{fig:shifts_summary}
highlight a few important points about ultracold, high-density
${}^{87}$Sr experiments and our low-energy effective theory.  First,
these experiments exhibit clear signatures of multi-body interactions,
as evidenced by a stark disagreement between the observed many-body
excitation energies $\Delta_{NX}$ and those that are predicted by the
two-body $\O\p{G}$ theory.  Multi-body interactions are thus crucial
for understanding these high-density experiments in the context of a
single-band Hubbard model, which naturally arises in the
zero-temperature limit when all atoms occupy their motional ground
state.  Second, the inter-atomic interactions in these experiments are
strong enough to require going beyond leading order for the
description of multi-body interactions in the low-energy effective
theory.  The formally small quantities organizing our perturbation
theory are two-body ground-state interaction energies (proportional to
the couplings $G_X$) divided by the spectral gap of the single-atom
Hamiltonian $H_0$.  These reduced (dimensionless) interaction energies
vary from $\sim0.05-0.15$ in the parameter regimes of the ${}^{87}$Sr
experiments considered here (see Appendix \ref{sec:pert_params}).  As
experiments begin to work with more atoms and different lattice
depths, therefore, reliably predicting interaction energies may
require going to yet higher orders in perturbation theory.  Due to a
combinatorial explosion of the number of diagrams which appear at
increasing orders in the effective theory, however, we need more
systematic methods to compute effective multi-body Hamiltonians at
fourth order.  In any case, we are agnostic as to whether such a
calculation would provide better agreement between experiment and
theory without first performing a detailed analysis of systematic
errors.

@@

\section*{Appendices}
\appendix
\setcounter{figure}{0}
\renewcommand\thefigure{\thesection.\arabic{figure}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Perturbative parameters for the effective theory}
\label{sec:pert_params}

The perturbative effective theory developed in Section
\ref{sec:low_energy} is organized in powers of the coupling constants
$G_X$.  The formally small, dimensionless quantities for this
perturbation theory are the two-body interaction energies $K G_X$,
where $K$ is a ground-state two-body overlap integral and $G_X$ is a
coupling constant, divided by the spectral gap $\Delta$ of the
non-interacting Hamiltonian $H_0$.  The quantities $K$, $G_X$, and
$\Delta$ all depend on the lattice depth $\U$.  Figure
\ref{fig:pert_params} shows these parameters for the case of
${}^{87}$Sr atoms with $X\in\set{\g\g, \e\g_-, \e\g_+, \e\e}$ at
lattice depths $\U\in\sp{30,80}E_{\t{R}}$, where
$E_{\t{R}}\approx3.5\times2\pi~\t{kHz}$ is the lattice photon recoil
energy of the atoms.  The fact that these perturbative parameters grow
with increasing lattice depth $\U$ is a consequence of the fact that
the overlap integral $K$ grows faster with $\U$ than the spectral gap
$\Delta$.  In the case of a harmonic trap with angular frequency
$\omega$, for example, these parameters would be
\begin{multline}
  \f{K_{\t{HO}} G_X}{\omega}
  = \f{G_X}{\omega} \int \d^3 x~\abs{\phi_{\t{HO}}}^4
  = \f{G_X}{\omega} \sp{\int \d x~
    \abs{\p{\f{\mA\omega}{\pi}}^{1/4} e^{-\mA\omega x^2/2}}^4}^3 \\
  \sim \f1{\omega}
  \sp{\omega \int\f{\d\p{\sqrt\omega x}}{\sqrt\omega}
    ~\abs{e^{-\mA\omega x^2/2}}^4}^3
  \propto \sqrt{\omega},
\end{multline}
where we assumed that the coupling constants $G_X$ vary weakly with
$\omega$.  While this result may seem to suggest that the low-energy
effective theory should become better at smaller lattice depths,
smaller lattice depths also result in increased theoretical
uncertainties from the growing relevance of the inter-site effects
discussed in Appendix \ref{sec:error}.

\begin{figure}
  \centering
  \includegraphics{perturbative_params.pdf}
  \caption{\footnotesize Dependence of the perturbative parameters
    $KG_X/\Delta$ on the lattice depth $\U$.}
  \label{fig:pert_params}
\end{figure}

@@

When restricted to the subspace of at most one orbital excitation per
lattice site, the $M$-body Hamiltonians of the low-energy effective
theory developed in Section \ref{sec:low_energy} can be written in the
form
\begin{align}
  H_M = \sum_{\abs{\set{\mu_j}}=M}
  \p{U_{M,\g} \n_{\mu_1,\g} \n_{\mu_2,\g}
    + U_{M,+} \n_{\mu_1,\e} \n_{\mu_2,\g}
    + U_{M,-} \c_{\mu_1,\g}^\dag \c_{\mu_2,\e}^\dag
    \c_{\mu_2,\g} \c_{\mu_1,\e}}
  \prod_{\alpha=3}^M \n_{\mu_\alpha,\g},
\end{align}
where the coefficients can be expanded as
$U_{MX} = \sum_p U_{MX}^{(p)}$ with terms $U_{MX}^{(p)}$ at order $p$
in the coupling constants $G_Y$.  The terms $U_{MX}^{(p)}$ can be
determined from the $M$-body $p$-order Hamiltonians $H_M^{(p)}$
derived in section \ref{sec:low_energy}, i.e.~in \eqref{eq:H_2},
\eqref{eq:H_3_2}, \eqref{eq:H_3_3}, and \eqref{eq:H_4_3}.  For the
effective 2-, 3-, and 4-body Hamiltonians through third order in the
coupling constants, the coefficients are
\begin{align}
  U_{2,\g} = \f12 \alpha_2^{(1)} G_\g,
  &&
  U_{2,+} = \alpha_2^{(1)} G_+,
  &&
  U_{2,-} = \alpha_2^{(1)} G_-,
\end{align}
\begin{align}
  U_{3,\g}^{(2)} = - \alpha_3^{(2)} G_\g^2,
  &&
  U_{3,+}^{(2)} = - \alpha_3^{(2)} G_+ \p{G_+ + 2 G_\g},
\end{align}
\begin{align}
  U_{3,-}^{(2)} = - \alpha_3^{(2)} G_- \p{2 G_+ + G_- + 2 G_\g},
\end{align}
\begin{align}
  U_{3,\g}^{(3)}
  = \p{\alpha_3^{(3)} - \alpha_5^{(3)}} 2 G_\g^3
  - \p{\alpha_{4,3}^{(3)} + \alpha_5^{(3)}} G_\g^3,
\end{align}
\begin{align}
  U_{3,+}^{(3)}
  &= \p{\alpha_3^{(3)} - \alpha_5^{(3)}} \p{G_+^3 + 4 G_+^2 G_\g
    + G_+ G_-^2 + G_+ G_\g^2 + G_-^3 + G_-^2 G_\g} \nonumber \\
  &\quad - \p{\alpha_{4,3}^{(3)} + \alpha_5^{(3)}}
  \p{G_+^3 + G_+^2 G_\g + G_+ G_-^2 + G_+ G_\g^2 + G_-^2 G_\g},
\end{align}
\begin{align}
  U_{3,-}^{(3)}
  &= \p{\alpha_3^{(3)} - \alpha_5^{(3)}} G_- \p{3 G_+^2
    + 2 G_+ G_- + 8 G_+ G_\g + 3 G_- G_\g + G_\g^2} \nonumber \\
  &\quad - \p{\alpha_{4,3}^{(3)} + \alpha_5^{(3)}}
  G_- \p{3 G_+^2 + 2 G_+ G_- + 2 G_+ G_\g + G_-^2 + G_\g^2},
\end{align}
\begin{align}
  U_{4,\g}^{(3)}
  = \p{\alpha_{4,1}^{(3)} - \alpha_5^{(3)}} G_\g^3
  + \p{\alpha_{4,2}^{(3)} - \alpha_5^{(3)}} 2 G_\g^3,
\end{align}
\begin{align}
  U_{4,+}^{(3)}
  &= \p{\alpha_{4,1}^{(3)} - \alpha_5^{(3)}}
  2 G_+ G_\g \p{G_+ + G_\g} \nonumber \\
  &\quad + \p{\alpha_{4,2}^{(3)} - \alpha_5^{(3)}}
  G_+ \p{G_+^2 + 2 G_+ G_\g + 5 G_\g^2},
\end{align}
\begin{align}
  U_{4,-}^{(3)}
  &= \p{\alpha_{4,1}^{(3)} - \alpha_5^{(3)}}
  2 G_- G_\g \p{2 G_+ + G_- + G_\g} \nonumber \\
  &\quad + \p{\alpha_{4,2}^{(3)} - \alpha_5^{(3)}}
  G_- \p{3 G_+^2 + 3 G_+ G_- + 4 G_+ G_\g + G_-^2
    + 2 G_- G_\g + 5 G_\g^2},
\end{align}
In terms of the spatial overlap integrals defined in \eqref{eq:K_klmn}
and \eqref{eq:K}, the prefactors $\alpha_X^{(p)}$ on the coefficients
$U_X^{(p)}$ are
\begin{align}
  \alpha_2^{(1)} \equiv K,
  &&
  \alpha_3^{(2)} \equiv \sum_{n>0} \f{K_n^2}{E_n},
  &&
  \alpha_3^{(3)} \equiv \sum_{\substack{\ell+m>0\\\ell+n>0}}
  \f{K_{\ell m} K^m_n K_{\ell n}}{E_{\ell m} E_{\ell n}},
\end{align}
\begin{align}
  \alpha_{4,1}^{(3)}
  \equiv \sum_{\substack{m\ge0\\n>0}} \f{K_{mn} K_m K_n}{E_{mn} E_n},
  &&
  \alpha_{4,2}^{(3)}
  \equiv \sum_{m,n>0} \f{K_m K^m_n K_n}{E_m E_n},
  &&
  \alpha_{4,3}^{(3)}
  \equiv K \sum_{m+n>0} \f{K_{mn}^2}{E_{mn}^2},
\end{align}
\begin{align}
  \alpha_5^{(3)}
  \equiv  K \sum_{n>0} \f{K_n^2}{E_n^2}.
\end{align}
